% https://github.com/arasgungore/arasgungore-CV/blob/main/main.tex
%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Mackenzie Goodwin} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:3213678901}{+1 (321) 367 8901}
    $|$
    \faAt \hspace{.5pt} \href{mailto:mackenziejgoodwin@outlook.com}{mackenziejgoodwin@outlook.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/mgoodwin-eth}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/mackenzieg}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{https://mackenzieg.tech/}{My Website}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://maps.app.goo.gl/kqi1WgTkcwmUqqwm8}{Palo Alto, CA}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {University of Waterloo
      % \normalfont{(Admission rate: 0.09\%)}
      }{Waterloo, Ontario, Canada}
      {Bachelor of Science in Electrical Engineering; \textbf{GPA: 3.58/4.00}}{Sep 2016 \textbf{--} June 2022}
      {}{} 

  \resumeSubHeadingListEnd


%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Languages:}{ Python, C, C++, Verilog, Verilog, Java, Javascript, Solidity } \\ \vspace{3pt}
        
        \textbf{Tools:}{ Cadence, Cocotb, Altium, Vivado, Cadence, Ansys HFSS, ModelSim} \\ \vspace{3pt}
        
        \textbf{Experience:}{ Network Protocols, RTL Design, Highspeed Design, Full Stack, Analog \& Digital Design} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd



%----------- EXPERIENCE -----------

\section{Experience}
\vspace{3pt}
\resumeSubHeadingListStart

  \resumeSubheading
    {Tesla Inc.}{Palo Alto, CA}
    {Senior Silicon Design Engineer}{Feb 2024 \textbf{--} Present}
    \resumeItemListStart
      \resumeItem{Innovated and developed the proprietary \href{https://patentimages.storage.googleapis.com/be/ad/28/d9a3cf28a032ae/WO2024039793A1.pdf}{Tesla Transport Protocol (TTP)} over Layer 3—a congestion-aware protocol enabling low-latency, high-throughput communication across DOJO’s fabric.}
      \resumeItem{Presented contributions to TTP at Hot Chips 2024; received patent recognition for protocol and silicon integration.}
      \resumeItem{Led design of custom high-density compute cluster integrating NICs to enable TTP-based communication.}
      \resumeItem{Collaborated across silicon, networking, and systems to optimize fabric-level throughput and scalability.}
    \resumeItemListEnd

  \resumeSubheading
    {Tesla Inc.}{Palo Alto, CA}
    {DOJO Hardware Engineering}{Jul 2022 \textbf{--} Feb 2024}
    \resumeItemListStart
      \resumeItem{Designed and integrated a custom NIC with PCIe, DDR, and 100G QSFP for TTP communication, presented at HotChips 2024.}
      \resumeItem{Optimized production line throughput via automation and end-of-line testers.}
      \resumeItem{Authored RTL, C++ drivers, and Node.js backend for hardware tracking and system diagnostics.}
      \resumeItem{Wrote RTL for I2C-to-AXI translation enabling microcontroller access to internal buses.}
      \resumeItem{Built automated silicon provisioning/test framework and debugged 50Gb/s SERDES & 100G QSFP interfaces.}
    \resumeItemListEnd

  \resumeSubheading
    {Tesla Inc.}{Palo Alto, CA}
    {DOJO Hardware Intern}{Aug 2021 \textbf{--} Dec 2021}
    \resumeItemListStart
      \resumeItem{Tested 100G QSFP and SERDES-based interface cards for DOJO mesh fabric and high-density power systems.}
      \resumeItem{Designed supercapacitor hot-swap controller enabling safe live insertion.}
      \resumeItem{Brought up Tesla's first DOJO compute cabinet and verified cabinet-wide integration.}
    \resumeItemListEnd

  \resumeSubheading
    {Tesla Inc.}{Palo Alto, CA}
    {Autopilot Hardware Intern}{Jan 2021 \textbf{--} May 2021}
    \resumeItemListStart
      \resumeItem{Built Python test suites for switch, GPS, and VRM bring-up to streamline validation workflows.}
      \resumeItem{Debugged Autopilot board failures in thermally stressed environments.}
      \resumeItem{Performed TDR and eye diagram analysis for SGMII and 1000Base-T1 interfaces.}
      \resumeItem{Validated buck converter transient/load stability.}
    \resumeItemListEnd

  \resumeSubheading
    {University of Waterloo}{Waterloo, ON, Canada}
    {Undergraduate Research Assistant}{Apr 2020 \textbf{--} Aug 2020}
    \resumeItemListStart
      \resumeItem{Developed 60GHz mmWave radar for non-contact hospital patient monitoring.}
      \resumeItem{Created DSP pipeline using wavelets/autocorrelation to detect breathing rates at 10m range.}
      \resumeItem{Built Python/C++ client-server system for real-time offloaded processing.}
    \resumeItemListEnd

  \resumeSubheading
    {Kazoo Technology}{Hong Kong, HK}
    {Electronics Designer Intern}{Aug 2019 \textbf{--} Apr 2020}
    \resumeItemListStart
      \resumeItem{Reversed engineered stylus touch hardware and validated via simulation and prototype.}
      \resumeItem{Designed analog amplifiers and touch spoofing systems with 200MSPS ADC on FPGA.}
    \resumeItemListEnd

  \resumeSubheading
    {AR Modular RF}{Seattle, WA}
    {RF Hardware Engineering Intern}{Jan 2019 \textbf{--} Apr 2019}
    \resumeItemListStart
      \resumeItem{Built LabView + Python-based automated RF test infrastructure, improving test speed and repeatability.}
      \resumeItem{Automated MAC management and firmware flashing system for IP-enabled RF products.}
      \resumeItem{Performed RF spec analysis and documented technical content for marketing.}
    \resumeItemListEnd

  \resumeSubheading
    {Evertz Microsystems}{Burlington, ON, Canada}
    {Systems Engineering Intern}{May 2018 \textbf{--} Aug 2018}
    \resumeItemListStart
      \resumeItem{Researched impedance/phase matching for 25G QSFP lanes to improve signal integrity.}
      \resumeItem{Captured RGMII, SGMII, and 1000BTX schematics with optimized magnetics and termination.}
      \resumeItem{Developed firmware for detecting encrypted video signals.}
    \resumeItemListEnd

  \resumeSubheading
    {Evertz Microsystems}{Burlington, ON, Canada}
    {Systems Engineering Intern}{Sep 2017 \textbf{--} Dec 2017}
    \resumeItemListStart
      \resumeItem{Created FPGA firmware for timestamped 10Gb/s packet capture and replay.}
      \resumeItem{Designed DDR3 buffer system with DMA for Wireshark-compatible frame dumping.}
      \resumeItem{Debugged PCB short circuits and engineered active fuse systems.}
    \resumeItemListEnd

  \resumeSubheading
    {Dozr}{Kitchener, ON, Canada}
    {Fullstack Software Engineer}{Jan 2017 \textbf{--} Apr 2017}
    \resumeItemListStart
      \resumeItem{Developed frontend React components and internal tooling using advanced state management.}
      \resumeItem{Built distributed Node.js/Python crawler with intelligent throttling and parallelism.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{High Honors Degree:}{ Awarded to Bachelor alumni who have graduated with a GPA greater than or equal to 3.50 by Boğaziçi University. (Jul 2023)} \\ \vspace{3pt}

        \textbf{TÜBİTAK 2247-C Intern Researcher Scholarship:}{ Awarded to students who take part in research projects carried out by the Scientific and Technological Research Council of Turkey (TÜBİTAK). (Dec 2021 \textbf{--} Jun 2022)} \\ \vspace{3pt}
    
        % \textbf{National University Admission Exam (YKS):}{ Ranked $75^{th}$ in Mathematics and Science among ca. 2.3 million candidates with a test score of 489.92/500. (Jul 2018)} \\ \vspace{3pt}
        
        \textbf{KYK Outstanding Success Scholarship:}{ Awarded to students who have been ranked in the top 100 on National University Admission Exam by Higher Education Credit and Hostels Institution (KYK). (Sep 2018 \textbf{--} Jun 2023)} \\ \vspace{3pt}
        
        % \textbf{Boğaziçi University Success Scholarship:}{ Awarded to students who have been ranked in the top 100 on National University Admission Exam by Boğaziçi University. (Sep 2018 \textbf{--} Jun 2023)} \\ \vspace{3pt}
        
        \textbf{Kocaeli Science High School Valedictorian Award:}{ Graduated as the highest ranked student. (Jun 2018)}
    }}
  \resumeSubHeadingListEnd



%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{Filters and Fractals} $|$ \emph{\href{https://github.com/arasgungore/filters-and-fractals}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{A C project which implements a variety of image processing operations that manipulate the size, filter, brightness, contrast, saturation, and other properties of PPM images from scratch and recursive fractal generation functions to model popular fractals including Mandelbrot set, Julia set, Koch curve, Barnsley fern, and Sierpinski triangle.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Chess Bot} $|$ \emph{\href{https://github.com/arasgungore/chess-bot}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{A C++ project in which you can play chess against an AI with a specified decision tree depth that uses alpha-beta pruning algorithm to predict the optimal move. Aside from basic moves, this mini chess engine also implements chess rules such as castling, en passant, fifty-move rule, threefold repetition, and pawn promotion.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{DS\&A Projects} $|$ \emph{\href{https://github.com/arasgungore/CMPE250-projects}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Five Java projects that apply DS\&A concepts such as discrete-event simulation using priority queues, Dijkstra's shortest path algorithm, Prim's algorithm to find the minimum spanning tree, Dinic's algorithm for maximum flow problems, and weighted job scheduling with dynamic programming to real-world problems.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd



%----------- RELEVANT COURSEWORK -----------

% \section{Relevant Coursework}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \small{\item{
        % \textbf{Major coursework:}{ Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering, Pattern Recognition, Introduction to Digital Signal Processing, Introduction to Digital Communications, Introduction to Database Systems, Introduction to Image Processing, Machine Vision} \\ \vspace{3pt}
        
        % \textbf{Minor coursework:}{ Discrete Computational Structures, Introduction to Object-Oriented Programming, Data Structures and Algorithms, Computer Organization, Fundamentals of Software Engineering}
    % }}
  % \resumeSubHeadingListEnd



%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
    
  % \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Basketball, Swimming, Fitness, Eight-ball, Horology}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \item{References available upon request.}
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}